---
title: "American Rescue Plan Act"

---
<style>


body {
  font-family: Arial,Helvetica,sans-serif;
}

.list-group-item.active,.list-group-item.active:focus, .list-group-item.active:hover {
background-color: #46b5d2;
border-color: #46b5d2;
}


.navbar-default .navbar-brand{
color:#333; 
font-weight: bold; !important
}

.navbar-default .navbar-brand:hover{
color: white; !important
font-weight: bold; !important
}

.navbar-default  {
background-color: #46b5d2;
border-color: #46b5d2;

}
.navbar-default .navbar-nav>li>a{
color:#333;
font-weight: bold;
}

.navbar-default .navbar-nav>li>a:hover{
color:white;
font-weight: bold;
}

.navbar-default .navbar-toggle {
border color: "#46b5d2";
}

#tocify-extend-page {
height: 80.797px; !important
}

</style>



## Budget



```{r eval=TRUE, echo = FALSE, message=FALSE, warning=FALSE, cache = TRUE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache=TRUE)

library(plyr)
library(tidyverse)
library(lubridate)
library(ggpubr)
library(plotly)
library(readxl)
library(flexdashboard)

arpa <- read_excel("arpa_funds_projects.xlsx", sheet = 2 )
arpa$Bucket[arpa$Bucket == "City Operations - Essential Worker Pay"] <- "Essential Worker Pay"
arpa$`Project/Program Name` [arpa$`Project/Program Name`  == "Homebuyer Acquisition Rehab Program"] <- "Homeowner Asst. Program"

arpa_budget <- arpa %>%
  #mutate_at(vars(Timestamp), list(as.character))%>%
  #filter(`Project/Program Name` != "Parking Garage")%>%
  count(Bucket, wt = Amount, name = "Budget")%>%
  mutate(Pct. = round(Budget/ sum(Budget)*100, 1))%>%
  

  ggplot(aes(x=Bucket, y = Budget, fill = Bucket))+
  geom_bar(stat = 'identity', color = "black")+
  scale_fill_brewer(palette = "Paired")+
  scale_y_continuous(label=scales::label_number_si(), limits = c(0, 20000000))+
  coord_flip()+
  geom_text(aes(label = paste(scales::comma(Budget, accuracy = 1.0), " ", "(", Pct., "%", ")",sep = "")),hjust = -0.1,  size = 3.5)+
  ylab("Budget (%)")+
  xlab("Buckets")+
  labs(
    title = "Total Budget--$35,914,130"
  )+
  theme_bw()+
  theme(legend.position = "none",
        legend.title = element_blank(),
        text = element_text(size = 13)) 
#       axis.title.y = element_blank())
#       axis.text = element_text(size = 9),
#       strip.text = element_text(size = 8),
#      plot.title = element_text(hjust = 0.5, size = 12, color = "black"))

arpa_budget

```


## Affordable Housing {.tabset}
### Budget

```{r eval=TRUE, echo = FALSE, message=FALSE, warning=FALSE, cache=FALSE}
#knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)


arpa_affordable <- arpa %>%
  filter(Bucket == "Affordable Housing")%>%
  dplyr::rename(Budget = Amount)%>%
  mutate(Pct. = round(Budget/ sum(Budget)*100, 1))%>%

  ggplot(aes(x=`Project/Program Name`, y = Budget, fill = Bucket))+
  geom_bar(stat = 'identity', color = "black")+
 scale_fill_manual(values = "#a6cee3")+
  scale_y_continuous(label=scales::label_number_si(), limits = c(0, 4000000))+
  coord_flip()+
  geom_text(aes(label = paste(scales::comma(Budget, accuracy = 1.0), " ", "(", Pct., "%", ")",sep = "")),hjust = -0.1,  size = 3.5)+
  ylab("Budget (%)")+
  #xlab("Buckets")+
  theme_bw()+
  theme(legend.position = "none",
        legend.title = element_blank(), 
        axis.title.y = element_blank(),
        text = element_text(size = 13))
#       axis.text = element_text(size = 9),
#       strip.text = element_text(size = 8),
#      plot.title = element_text(hjust = 0.5, size = 12, color = "black"))

arpa_affordable

```

### Spending Summary

**COMING SOON!**

```{r eval=TRUE, echo = FALSE, message=FALSE, warning=FALSE, cache = FALSE, out.width='100%'}

affordable_gauge <- plot_ly(
    domain = list(x = c(0, 0.6), y = FALSE),
    value = 0, 
    title = list(text = "3.35M Budget"),
    type = "indicator",
    mode = "gauge+number", height = 250, 
    gauge = list(
      axis =list(range = list(NULL, 3350000)),
      #steps = list(
      #  list(range = c(0, 250), color = "lightgray"),
      #  list(range = c(250, 400), color = "gray")),
      threshold = list(
        line = list(color = "red", width = 4),
        thickness = 0.75,
        value = 3350000)))



affordable_gauge <- affordable_gauge %>%
  config(displayModeBar = F, responsive = TRUE)%>%
    layout(margin = list(l=20,r=20, t=50, b=20, pad = 0),
         font = list(size = 12))

affordable_gauge
#export(affordable_gauge, "_site/affordable_gauge1.png")
#orca(affordable_gauge, file = "_site/affordable_gauge1.png",  )
#margin = list(l=20,r=30)


```


## Essential Worker Pay {.tabset}
### Budget

```{r eval=TRUE, echo = FALSE, message=FALSE, cache=FALSE, warning=FALSE}
#knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

arpa_essn_wrk <- arpa %>%
  filter(Bucket == "Essential Worker Pay")%>%
  dplyr::rename(Budget = Amount)%>%
  mutate(Pct. = round(Budget/ sum(Budget)*100, 1))%>%

  ggplot(aes(x=`Project/Program Name`, y = Budget, fill = Bucket))+
  geom_bar(stat = 'identity', color = "black")+
  scale_fill_manual(values = "#33a02c")+
  scale_y_continuous(label=scales::label_number_si(), limits = c(0, 4000000))+
  coord_flip()+
  geom_text(aes(label = paste(scales::comma(Budget, accuracy = 1.0), " ", "(", Pct., "%", ")",sep = "")),hjust = -0.1,  size = 3.5)+
  ylab("Budget (%)")+
  #xlab("Buckets")+
  theme_bw()+
  theme(legend.position = "none",
        legend.title = element_blank(), 
        axis.title.y = element_blank(),
        text = element_text(size = 13))
#       axis.text = element_text(size = 9),
#       strip.text = element_text(size = 8),
#      plot.title = element_text(hjust = 0.5, size = 12, color = "black"))

arpa_essn_wrk

```

### Spending Summary


```{r eval=TRUE, echo = FALSE, message=FALSE, warning=FALSE, cache=TRUE, out.width='100%'}

essential_gauge <- plot_ly(
    domain = list(x = c(0, 0.6), y = FALSE),
    value = 2350082.67, 
    title = list(text = "2.50M Budget"),
    type = "indicator",
    mode = "gauge+number", height = 250,
    gauge = list(
      axis =list(range = list(NULL, 2504000)),
      #steps = list(
      #  list(range = c(0, 250), color = "lightgray"),
      #  list(range = c(250, 400), color = "gray")),
      threshold = list(
        line = list(color = "red", width = 4),
        thickness = 0.75,
        value = 2504000)))

essential_gauge <- essential_gauge %>%
  config(displayModeBar = F, responsive = TRUE)%>%
  layout(margin = list(l=20,r=20, t=50, b=20, pad = 0),
         font = list(size = 12))

essential_gauge

```

## City Operations {.tabset}
### Budget

```{r eval=TRUE, echo = FALSE, message=FALSE, cache=FALSE, warning=FALSE}
#knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

arpa_ctyop <- arpa %>%
  filter(Bucket == "City Operations")%>%
  dplyr::rename(Budget = Amount)%>%
  mutate(Pct. = round(Budget/ sum(Budget)*100, 1))%>%

  ggplot(aes(x=`Project/Program Name`, y = Budget, fill = Bucket))+
  geom_bar(stat = 'identity', color = "black")+
  scale_fill_manual(values = "#1f78b4")+
  scale_y_continuous(label=scales::label_number_si(), limits = c(0, 4000000))+
  coord_flip()+
  geom_text(aes(label = paste(scales::comma(Budget, accuracy = 1.0), " ", "(", Pct., "%", ")",sep = "")),hjust = -0.1,  size = 3.5)+
  ylab("Budget (%)")+
  #xlab("Buckets")+
  theme_bw()+
  theme(legend.position = "none",
        legend.title = element_blank(), 
        axis.title.y = element_blank(),
        text = element_text(size = 13))
#       axis.text = element_text(size = 9),
#       strip.text = element_text(size = 8),
#      plot.title = element_text(hjust = 0.5, size = 12, color = "black"))

arpa_ctyop

```

### Spending Summary

```{r eval=TRUE, echo = FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%'}

ctyops_gauge <- plot_ly(
    domain = list(x = c(0, 0.6), y = FALSE),
    value = 583900, 
    title = list(text = "1.45M Budget"),
    type = "indicator",
    mode = "gauge+number", height = 250,
    gauge = list(
      axis =list(range = list(NULL, 1455000)),
      #steps = list(
      #  list(range = c(0, 250), color = "lightgray"),
      #  list(range = c(250, 400), color = "gray")),
      threshold = list(
        line = list(color = "red", width = 4),
        thickness = 0.75,
        value = 1455000)))

ctyops_gauge <- ctyops_gauge %>%
  config(displayModeBar = F, responsive = TRUE)%>%
  layout(margin = list(l=20,r=20, t=50, b=20, pad = 0),
         font = list(size = 12))

ctyops_gauge

```


## Replace Revenue {.tabset}
### Budget

```{r eval=TRUE, echo = FALSE, message=FALSE, cache=FALSE, warning=FALSE}
#knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

repl_rev <- arpa %>%
  filter(Bucket == "Replace Revenue")%>%
  dplyr::rename(Budget = Amount)%>%
  mutate(Pct. = round(Budget/ sum(Budget)*100, 1))%>%

  ggplot(aes(x=`Project/Program Name`, y = Budget, fill = Bucket))+
  geom_bar(stat = 'identity', color = "black")+
  scale_fill_manual(values = "#cab2d6")+
  scale_y_continuous(label=scales::label_number_si(), limits = c(0, 17000000))+
  coord_flip()+
  geom_text(aes(label = paste(scales::comma(Budget, accuracy = 1.0), " ", "(", Pct., "%", ")",sep = "")),hjust = -0.1,  size = 3.5)+
  ylab("Budget (%)")+
  #xlab("Buckets")+
  theme_bw()+
  theme(legend.position = "none",
        legend.title = element_blank(), 
        axis.title.y = element_blank(),
        text = element_text(size = 13))
#       axis.text = element_text(size = 9),
#       strip.text = element_text(size = 8),
#      plot.title = element_text(hjust = 0.5, size = 12, color = "black"))

repl_rev

```


### Spending Summary

**COMING SOON!**

```{r eval=TRUE, echo = FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%'}

reprev_gauge <- plot_ly(
    domain = list(x = c(0, 0.6), y = FALSE),
    value = 1, 
    title = list(text = "12.5M Budget"),
    type = "indicator",
    mode = "gauge+number", height = 250,
    gauge = list(
      axis =list(range = list(NULL, 12500000)),
      #steps = list(
      #  list(range = c(0, 250), color = "lightgray"),
      #  list(range = c(250, 400), color = "gray")),
      threshold = list(
        line = list(color = "red", width = 4),
        thickness = 0.75,
        value = 12500000)))

reprev_gauge <- reprev_gauge %>%
  config(displayModeBar = F, responsive = TRUE)%>%
  layout(margin = list(l=20,r=20, t=50, b=20, pad = 0),
         font = list(size = 12))

reprev_gauge

```

## Community Outreach {.tabset}
### Budget

```{r eval=TRUE, echo = FALSE, message=FALSE, cache = FALSE, warning=FALSE}
#knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

comm_out <- arpa %>%
  filter(Bucket == "Community Outreach")%>%
  dplyr::rename(Budget = Amount)%>%
  mutate(Pct. = round(Budget/ sum(Budget)*100, 1))%>%

  ggplot(aes(x=`Project/Program Name`, y = Budget, fill = Bucket))+
  geom_bar(stat = 'identity', color = "black")+
  scale_fill_manual(values = "#b2df8a")+
  scale_y_continuous(label=scales::label_number_si(), limits = c(0, 100000))+
  coord_flip()+
  geom_text(aes(label = paste(scales::comma(Budget, accuracy = 1.0), " ", "(", Pct., "%", ")",sep = "")),hjust = -0.1,  size = 3.5)+
  ylab("Budget (%)")+
  #xlab("Buckets")+
  theme_bw()+
  theme(legend.position = "none",
        legend.title = element_blank(), 
        axis.title.y = element_blank(),
        text = element_text(size = 13))
#       axis.text = element_text(size = 9),
#       strip.text = element_text(size = 8),
#      plot.title = element_text(hjust = 0.5, size = 12, color = "black"))

comm_out

```

### Spending Summary

**COMING SOON!**

```{r eval=TRUE, echo = FALSE, message=FALSE, warning=FALSE, cache = FALSE, out.width='100%'}

comout_gauge <- plot_ly(
    domain = list(x = c(0, 0.6), y = FALSE),
    value = 0, 
    title = list(text = "80K Budget"),
    type = "indicator",
    mode = "gauge+number", height = 250,
    gauge = list(
      axis =list(range = list(NULL, 80000)),
      #steps = list(
      #  list(range = c(0, 250), color = "lightgray"),
      #  list(range = c(250, 400), color = "gray")),
      threshold = list(
        line = list(color = "red", width = 4),
        thickness = 0.75,
        value = 80000)))

comout_gauge <- comout_gauge %>%
  config(displayModeBar = F, responsive = TRUE)%>%
  layout(margin = list(l=20,r=20, t=50, b=20, pad = 0),
         font = list(size = 12))

comout_gauge

```

## Expand Access to Wi-Fi {.tabset}
### Budget

```{r eval=TRUE, echo = FALSE, message=FALSE, cache = TRUE, warning=FALSE}
#knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

wifi_accs <- arpa %>%
  filter(Bucket == "Expand Access to Wi-Fi")%>%
  dplyr::rename(Budget = Amount)%>%
  mutate(Pct. = round(Budget/ sum(Budget)*100, 1))%>%

  ggplot(aes(x=`Project/Program Name`, y = Budget, fill = Bucket))+
  geom_bar(stat = 'identity', color = "black")+
  scale_fill_manual(values = "#fb9a99")+
  scale_y_continuous(label=scales::label_number_si(), limits = c(0, 800000))+
  coord_flip()+
  geom_text(aes(label = paste(scales::comma(Budget, accuracy = 1.0), " ", "(", Pct., "%", ")",sep = "")),hjust = -0.1,  size = 3.5)+
  ylab("Budget (%)")+
  #xlab("Buckets")+
  theme_bw()+
  theme(legend.position = "none",
        legend.title = element_blank(), 
        axis.title.y = element_blank(),
        text = element_text(size = 13))
#       axis.text = element_text(size = 9),
#       strip.text = element_text(size = 8),
#      plot.title = element_text(hjust = 0.5, size = 12, color = "black"))

wifi_accs

```

### Spending Summary

**COMING SOON!**

```{r eval=TRUE, echo = FALSE, message=FALSE, warning=FALSE, cache = TRUE, out.width='100%'}

wifi_gauge <- plot_ly(
    domain = list(x = c(0, 0.6), y = FALSE),
    value = 0, 
    title = list(text = "455K Budget"),
    type = "indicator",
    mode = "gauge+number", height = 250,
    gauge = list(
      axis =list(range = list(NULL, 455000)),
      #steps = list(
      #  list(range = c(0, 250), color = "lightgray"),
      #  list(range = c(250, 400), color = "gray")),
      threshold = list(
        line = list(color = "red", width = 4),
        thickness = 0.75,
        value = 455000)))

wifi_gauge <- wifi_gauge %>%
  config(displayModeBar = F, responsive = TRUE)%>%
  layout(margin = list(l=20,r=20, t=50, b=20, pad = 0),
         font = list(size = 12))

wifi_gauge

```

## Job Training Assistance {.tabset}

### Budget

```{r eval=TRUE, echo = FALSE, message=FALSE, cache = TRUE, warning=FALSE}
#knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

jta <- arpa %>%
  filter(Bucket == "Job Training Assistance")%>%
  dplyr::rename(Budget = Amount)%>%
  mutate(Pct. = round(Budget/ sum(Budget)*100, 1))%>%

  ggplot(aes(x=`Project/Program Name`, y = Budget, fill = Bucket))+
  geom_bar(stat = 'identity', color = "black")+
  scale_fill_manual(values = "#e31a1c")+
  scale_y_continuous(label=scales::label_number_si(), limits = c(0, 600000))+
  coord_flip()+
  geom_text(aes(label = paste(scales::comma(Budget, accuracy = 1.0), " ", "(", Pct., "%", ")",sep = "")),hjust = -0.1,  size = 3.5)+
  ylab("Budget (%)")+
  #xlab("Buckets")+
  theme_bw()+
  theme(legend.position = "none",
        legend.title = element_blank(), 
        axis.title.y = element_blank(),
        text = element_text(size = 13))
#       axis.text = element_text(size = 9),
#       strip.text = element_text(size = 8),
#      plot.title = element_text(hjust = 0.5, size = 12, color = "black"))

jta

```


### Spending Summary

**COMING SOON!**

```{r eval=TRUE, echo = FALSE, message=FALSE, warning=FALSE, cache = TRUE, out.width='100%'}

jta_gauge <- plot_ly(
    domain = list(x = c(0, 0.6), y = FALSE),
    value = 0, 
    title = list(text = "375K Budget"),
    type = "indicator",
    mode = "gauge+number", height = 250,
    gauge = list(
      axis =list(range = list(NULL, 375000)),
      #steps = list(
      #  list(range = c(0, 250), color = "lightgray"),
      #  list(range = c(250, 400), color = "gray")),
      threshold = list(
        line = list(color = "red", width = 4),
        thickness = 0.75,
        value = 375000)))

jta_gauge <- jta_gauge %>%
  config(displayModeBar = F, responsive = TRUE)%>%
  layout(margin = list(l=20,r=20, t=50, b=20, pad = 0),
         font = list(size = 12))

jta_gauge

```


## Neighborhood Projects {.tabset}

### Budget

```{r eval=TRUE, echo = FALSE, message=FALSE, cache = TRUE, warning=FALSE}
#knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

np <- arpa %>%
  filter(Bucket == "Neighborhood Projects")%>%
  dplyr::rename(Budget = Amount)%>%
  mutate(Pct. = round(Budget/ sum(Budget)*100, 1))%>%

  ggplot(aes(x=`Project/Program Name`, y = Budget, fill = Bucket))+
  geom_bar(stat = 'identity', color = "black")+
  scale_fill_manual(values = "#fdbf6f")+
  scale_y_continuous(label=scales::label_number_si(), limits = c(0, 2000000))+
  coord_flip()+
  geom_text(aes(label = paste(scales::comma(Budget, accuracy = 1.0), " ", "(", Pct., "%", ")",sep = "")),hjust = -0.1,  size = 3.5)+
  ylab("Budget (%)")+
  #xlab("Buckets")+
  theme_bw()+
  theme(legend.position = "none",
        legend.title = element_blank(), 
        axis.title.y = element_blank(),
        text = element_text(size = 13))
#       axis.text = element_text(size = 9),
#       strip.text = element_text(size = 8),
#      plot.title = element_text(hjust = 0.5, size = 12, color = "black"))

np

```

### Spending Summary

**COMING SOON!**

```{r eval=TRUE, echo = FALSE, message=FALSE, warning=FALSE, cache = TRUE, out.width='100%'}

np_gauge <- plot_ly(
    domain = list(x = c(0, 0.6), y = FALSE),
    value = 0, 
    title = list(text = "2.38M Budget"),
    type = "indicator",
    mode = "gauge+number", height = 250,
    gauge = list(
      axis =list(range = list(NULL, 2500000)),
      #steps = list(
      #  list(range = c(0, 250), color = "lightgray"),
      #  list(range = c(250, 400), color = "gray")),
      threshold = list(
        line = list(color = "red", width = 4),
        thickness = 0.75,
        value = 2379130)))

np_gauge <- np_gauge %>%
  config(displayModeBar = F, responsive = TRUE)%>%
  layout(margin = list(l=20,r=20, t=50, b=20, pad = 0),
         font = list(size = 12))

np_gauge

```


## Public Health {.tabset}

### Budget

```{r eval=TRUE, echo = FALSE, message=FALSE, cache = TRUE, warning=FALSE}
#knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

pub_health <- arpa %>%
  filter(Bucket == "Public Health")%>%
  dplyr::rename(Budget = Amount)%>%
  mutate(Pct. = round(Budget/ sum(Budget)*100, 1))%>%

  ggplot(aes(x=`Project/Program Name`, y = Budget, fill = Bucket))+
  geom_bar(stat = 'identity', color = "black")+
  scale_fill_manual(values = "#ff7f00")+
  scale_y_continuous(label=scales::label_number_si(), limits = c(0, 4000000))+
  coord_flip()+
  geom_text(aes(label = paste(scales::comma(Budget, accuracy = 1.0), " ", "(", Pct., "%", ")",sep = "")),hjust = -0.1,  size = 3.5)+
  ylab("Budget (%)")+
  #xlab("Buckets")+
  theme_bw()+
  theme(legend.position = "none",
        legend.title = element_blank(), 
        axis.title.y = element_blank(),
        text = element_text(size = 13))
#       axis.text = element_text(size = 9),
#       strip.text = element_text(size = 8),
#      plot.title = element_text(hjust = 0.5, size = 12, color = "black"))

pub_health

```

### Spending Summary

**COMING SOON!**

```{r eval=TRUE, echo = FALSE, message=FALSE, warning=FALSE, cache = TRUE, out.width='100%'}

ph_gauge <- plot_ly(
    domain = list(x = c(0, 0.6), y = FALSE),
    value = 0, 
    title = list(text = "3.75M Budget"),
    type = "indicator",
    mode = "gauge+number", height = 250,
    gauge = list(
      axis =list(range = list(NULL, 3750000)),
      #steps = list(
      #  list(range = c(0, 250), color = "lightgray"),
      #  list(range = c(250, 400), color = "gray")),
      threshold = list(
        line = list(color = "red", width = 4),
        thickness = 0.75,
        value = 3750000)))

ph_gauge <- ph_gauge %>%
  config(displayModeBar = F, responsive = TRUE)%>%
  layout(margin = list(l=20,r=20, t=50, b=20, pad = 0),
         font = list(size = 12))

ph_gauge

```


## Small Business Assistance {.tabset}

### Budget

```{r eval=TRUE, echo = FALSE, message=FALSE, cache = TRUE, warning=FALSE}
#knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

sba <- arpa %>%
  filter(Bucket == "Small Business Assistance")%>% #& `Project/Program Name` != "Parking Garage")%>%
  dplyr::rename(Budget = Amount)%>%
  mutate(Pct. = round(Budget/ sum(Budget)*100, 1))%>%

  ggplot(aes(x=`Project/Program Name`, y = Budget, fill = Bucket))+
  geom_bar(stat = 'identity', color = "black")+
  scale_fill_manual(values = "#6a3d9a")+
  scale_y_continuous(label=scales::label_number_si(), limits = c(0, 10000000))+
  coord_flip()+
  geom_text(aes(label = paste(scales::comma(Budget, accuracy = 1.0), " ", "(", Pct., "%", ")",sep = "")),hjust = -0.1,  size = 3.5)+
  ylab("Budget (%)")+
  #xlab("Buckets")+
  theme_bw()+
  theme(legend.position = "none",
        legend.title = element_blank(), 
        axis.title.y = element_blank(),
        text = element_text(size = 13))
#       axis.text = element_text(size = 9),
#       strip.text = element_text(size = 8),
#      plot.title = element_text(hjust = 0.5, size = 12, color = "black"))

sba

```

### Spending Summary

**COMING SOON!**

```{r eval=TRUE, echo = FALSE, message=FALSE, warning=FALSE, cache = TRUE, out.width='100%'}

sba_gauge <- plot_ly(
    domain = list(x = c(0, 0.6), y = FALSE),
    value = 0, 
    title = list(text = "7.6M Budget"),
    type = "indicator",
    mode = "gauge+number", height = 250,
    gauge = list(
      axis =list(range = list(NULL, 7600000)),
      #steps = list(
      #  list(range = c(0, 250), color = "lightgray"),
      #  list(range = c(250, 400), color = "gray")),
      threshold = list(
        line = list(color = "red", width = 4),
        thickness = 0.75,
        value = 7600000)))

sba_gauge <- sba_gauge %>%
  config(displayModeBar = F, responsive = TRUE)%>%
  layout(margin = list(l=20,r=20, t=50, b=20, pad = 0),
         font = list(size = 12))

sba_gauge

```

## Social Services {.tabset}

### Budget

```{r eval=TRUE, echo = FALSE, message=FALSE, cache = TRUE, warning=FALSE}
#knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

soc_serv <- arpa %>%
  filter(Bucket == "Social Services")%>%
  dplyr::rename(Budget = Amount)%>%
  mutate(Pct. = round(Budget/ sum(Budget)*100, 1))%>%

  ggplot(aes(x=`Project/Program Name`, y = Budget, fill = Bucket))+
  geom_bar(stat = 'identity', color = "black")+
  scale_fill_manual(values = "#ffff99")+
  scale_y_continuous(label=scales::label_number_si(), limits = c(0, 3000000))+
  coord_flip()+
  geom_text(aes(label = paste(scales::comma(Budget, accuracy = 1.0), " ", "(", Pct., "%", ")",sep = "")),hjust = -0.1,  size = 3.5)+
  ylab("Budget (%)")+
  #xlab("Buckets")+
  theme_bw()+
  theme(legend.position = "none",
        legend.title = element_blank(), 
        axis.title.y = element_blank(),
        text = element_text(size = 13))
#       axis.text = element_text(size = 9),
#       strip.text = element_text(size = 8),
#      plot.title = element_text(hjust = 0.5, size = 12, color = "black"))

soc_serv

```

### Spending Summary

**COMING SOON!**

```{r eval=TRUE, echo = FALSE, message=FALSE, warning=FALSE, cache = TRUE, out.width='100%'}

socserv_gauge <- plot_ly(
    domain = list(x = c(0, 0.6), y = FALSE),
    value = 0, 
    title = list(text = "1.43M Budget"),
    type = "indicator",
    mode = "gauge+number", height = 250,
    gauge = list(
      axis =list(range = list(NULL, 1425000)),
      #steps = list(
      #  list(range = c(0, 250), color = "lightgray"),
      #  list(range = c(250, 400), color = "gray")),
      threshold = list(
        line = list(color = "red", width = 4),
        thickness = 0.75,
        value = 1425000)))

socserv_gauge <- socserv_gauge %>%
  config(displayModeBar = F, responsive = TRUE)%>%
  layout(margin = list(l=20,r=20, t=50, b=20, pad = 0),
         font = list(size = 12))

socserv_gauge

```

## Tourism {.tabset}

### Budget

```{r eval=TRUE, echo = FALSE, message=FALSE, cache = TRUE, warning=FALSE}
#knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

tourism <- arpa %>%
  filter(Bucket == "Tourism")%>%
  dplyr::rename(Budget = Amount)%>%
  mutate(Pct. = round(Budget/ sum(Budget)*100, 1))%>%

  ggplot(aes(x=`Project/Program Name`, y = Budget, fill = Bucket))+
  geom_bar(stat = 'identity', color = "black")+
  scale_fill_manual(values = "#b15928")+
  scale_y_continuous(label=scales::label_number_si(), limits = c(0, 80000))+
  coord_flip()+
  geom_text(aes(label = paste(scales::comma(Budget, accuracy = 1.0), " ", "(", Pct., "%", ")",sep = "")),hjust = -0.1,  size = 3.5)+
  ylab("Budget (%)")+
  #xlab("Buckets")+
  theme_bw()+
  theme(legend.position = "none",
        legend.title = element_blank(), 
        axis.title.y = element_blank(),
        text = element_text(size = 13))
#       axis.text = element_text(size = 9),
#       strip.text = element_text(size = 8),
#      plot.title = element_text(hjust = 0.5, size = 12, color = "black"))

tourism

```

### Spending Summary

```{r eval=TRUE, echo = FALSE, message=FALSE, warning=FALSE, cache = TRUE, out.width='100%'}

tourism_gauge <- plot_ly(
    domain = list(x = c(0, 0.6), y = FALSE),
    value = 41000, 
    title = list(text = "41K Budget"),
    type = "indicator",
    mode = "gauge+number", height = 250,
    gauge = list(
      axis =list(range = list(NULL, 41000)),
      #steps = list(
      #  list(range = c(0, 250), color = "lightgray"),
      #  list(range = c(250, 400), color = "gray")),
      threshold = list(
        line = list(color = "red", width = 4),
        thickness = 0.75,
        value = 41000)))

tourism_gauge <- tourism_gauge %>%
  config(displayModeBar = F, responsive = TRUE)%>%
  layout(margin = list(l=20,r=20, t=50, b=20, pad = 0),
         font = list(size = 12))

tourism_gauge



```
